---
title: "SDS 315 Homework 4"
author: "Tommy Fang EID: hf5829 Repo: https://github.com/tominister/SDS315"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(minpack.lm)
library(mosaic)
options(scipen=999)
prices <- read.csv("gasprices.csv")
cars <- read.csv("sclass.csv")
shows <- read.csv("nbc_pilotsurvey.csv")
ebay <- read.csv("ebay.csv")
```

## Problem 1
#### Part A
```{r, echo=F, warning=F, message=F}
diffmean(Price~Competitors, data=prices)
boot_competitors <- do(10000)*diffmean(Price~Competitors, data=mosaic::resample(prices, replace=T))
ggplot(data=boot_competitors)+geom_histogram(aes(x=diffmean))+labs(title="Histogram for Difference in Mean between Gas Prices based on Competition", x="Difference in Mean Price")
conf <- confint(boot_competitors, level=0.95)
conf
```
Competition does not seem to affect gas prices. Based on the data above, the actual difference in mean between the gas prices with competition and without competition in the sample is -0.023 and the estimate is somewhere between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. Since 0 is included within the confidence interval, the difference in means is not statistically significant to support the theory. 

#### Part B
```{r, echo=F, warning=F, message=F}
income_model <- lm(Price~Income, data=prices)
ggplot(income_model)+geom_point(aes(x=Income,y=Price))+geom_smooth(aes(x=Income,y=Price), method='lm')+labs(title="Linear Model for Gas Price and Median Household Income", x="Median Income", y="Gas Price")
coef(income_model)
boot_income <- do(10000)*coef(lm(Price~Income, data=mosaic::resample(prices, replace=T)))[2]
conf <- confint(boot_income, level=0.95)
conf
```
Income does seem to affect gas prices. Based on the data above, the slope in the linear model of gas prices and median income in the sample is 1.248e-06 and the estimate is somewhere between `r conf$lower` and `r conf$upper` with 95% confidence. Since 0 is not included within the confidence interval, the slope is statistically significant to support the theory. 

#### Part C
```{r, echo=F, warning=F, message=F}
diffmean(Price~Stoplight, data=prices)
boot_stoplight <- do(10000)*diffmean(Price~Stoplight, data=mosaic::resample(prices, replace=T))
ggplot(data=boot_stoplight)+geom_histogram(aes(x=diffmean))+labs(title="Histogram for Difference in Mean between Gas Prices based on Stoplights", x="Difference in Mean Price")
conf <- confint(boot_stoplight, level=0.95)
conf
```
Stoplights do not seem to affect gas prices. Based on the data above, the actual difference in mean between the gas prices with stoplights and without stoplights in the sample is -0.003 and the estimate is somewhere between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. Since 0 is included within the confidence interval, the difference in means is not statistically significant to support the theory. 

#### Part D
```{r, echo=F, warning=F, message=F}
diffmean(Price~Highway, data=prices)
boot_highway <- do(10000)*diffmean(Price~Highway, data=mosaic::resample(prices, replace=T))
ggplot(data=boot_highway)+geom_histogram(aes(x=diffmean))+labs(title="Histogram for Difference in Mean between Gas Prices based on Highways", x="Difference in Mean Price")
conf <- confint(boot_highway, level=0.95)
conf
```
Highways do seem to affect gas prices. Based on the data above, the actual difference in mean between the gas prices with highways and without highways in the sample is 0.046 and the estimate is somewhere between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. Since 0 is not included within the confidence interval, the difference in means is statistically significant to support the theory. 

#### Part E
```{r, echo=F, warning=F, message=F}
prices$Shell <- prices$Brand=='Shell'
diffmean(Price~Shell, data=prices)
boot_shell<- do(10000)*diffmean(Price~Shell, data=mosaic::resample(prices, replace=T))
ggplot(data=boot_shell)+geom_histogram(aes(x=diffmean))+labs(title="Histogram for Difference in Mean between Gas Prices based on Shell", x="Difference in Mean Price")
conf <- confint(boot_shell, level=0.95)
conf
```
Shell does not seem to affect gas prices. Based on the data above, the actual difference in mean between the gas prices with Shell and without Shell in the sample is 0.027 and the estimate is somewhere between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. Since 0 is included within the confidence interval, the difference in means is not statistically significant to support the theory. 

## Problem 2
#### Part A
```{r, echo=F, warning=F, message=F}
filterA<-filter(cars, year==2011&trim == "63 AMG"&condition=="Used")
mean(~mileage, data=filterA)
boot_used<- do(10000)*mean(~mileage, data=mosaic::resample(filterA, replace=T))
ggplot(data=boot_used)+geom_histogram(aes(x=mean))+labs(title="Histogram for Mean Mileage for Used 63 AMG Mercedes in 2011", x="Mean Mileage")
conf <- confint(boot_used, level=0.95)
conf
```
The average mileage obtained from the filtered sample is 30763.56 and the estimated mileage is between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. 

#### Part B
```{r, echo=F, warning=F, message=F}
cars$black <- cars$color=="Black"
filterB<-filter(cars, year==2014&trim == "550")
prop(~black, data=filterB)
boot_black<- do(10000)*prop(~black, data=mosaic::resample(filterB, replace=T))
ggplot(data=boot_black)+geom_histogram(aes(x=prop_TRUE))+labs(title="Histogram for Proportion of Black 550 Trim Mercedes in 2014", x="Proportion Black")
conf <- confint(boot_black, level=0.95)
conf
```
The proportion of black Mercedes obtained from the filtered sample is 0.435 and the estimated proportion is between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. 

## Problem 3
#### Part A
```{r, echo=F, warning=F, message=F}
filterA <- filter(shows, Show == "Living with Ed" | Show == "My Name is Earl")
diffmean(Q1_Happy~Show, data=filterA)
boot_happy <- do(10000)*diffmean(Q1_Happy~Show, data=mosaic::resample(filterA, replace=T))
ggplot(data=boot_happy)+geom_histogram(aes(x=diffmean))+labs(title="Histogram for Difference in Mean between Viewer Happiness based on Show", x="Difference in Mean Happiness")
conf <- confint(boot_happy, level=0.95)
conf
```
The question we will answer is whether or not the show Living with Ed produces more viwer happiness than My Name is Earl or vice versa. We first calculate the actual mean difference and then filter the entire dataset into containing these two shows and then bootstrap sample 10000 times using the functions filter and do(10000) and resample() respectively. Then we use ggplot to plot a histogram of the distribution of mean differences from the bootstrap and confint() to observe the confidence interval at 95%. The two shows does not seem be statistically significant for viewer happiness. Based on the data above, the actual difference in mean between the happiness for Living with Ed and My Name is Earl is -0.149 in the sample and the estimate is somewhere between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. Since 0 is included within the confidence interval, the difference in means is not statistically significant, meaning no show produces a significantly higher mean happiness among viewers. 

#### Part B
```{r, echo=F, warning=F, message=F}
filterB <- filter(shows, Show == "The Biggest Loser" | Show == "The Apprentice: Los Angeles")
diffmean(Q1_Annoyed~Show, data=filterB)
boot_annoyed <- do(10000)*diffmean(Q1_Annoyed~Show, data=mosaic::resample(filterB, replace=T))
ggplot(data=boot_annoyed)+geom_histogram(aes(x=diffmean))+labs(title="Histogram for Difference in Mean between Viewer Annoyance based on Show", x="Difference in Mean Annoyance")
conf <- confint(boot_annoyed, level=0.95)
conf
```
The question we will answer is whether or not the show The Biggest Loser produces more viwer annoyance than The Apprentice: Los Angeles or vice versa. WWe first calculate the actual mean difference and then filter the entire dataset into containing these two shows and then bootstrap sample 10000 times using the functions filter and do(10000) and resample() respectively. Then we use ggplot to plot a histogram of the distribution of mean differences from the bootstrap and confint() to observe the confidence interval at 95%. The two shows do seem to be statistically significant for viewer annoyance. Based on the data above, the actual difference in mean between the annoyance for the two shows is -0.271 in the sample and the estimate is somewhere between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. Since 0 is not included within the confidence interval, the difference in means is statistically significant, meaning one show produces a significantly higher mean annoyance among viewers. 

#### Part C
```{r, echo=F, warning=F, message=F}
shows$confusing <- shows$Q2_Confusing>=4
filterC <- filter(shows, Show == "Dancing with the Stars")
prop(~confusing, data=filterC)
boot_confused <- do(10000)*prop(~confusing, data=mosaic::resample(filterC, replace=T))
ggplot(data=boot_confused)+geom_histogram(aes(x=prop_TRUE))+labs(title="Histogram for Proportion of Confused Viewers Watching Dancing with the Stars", x="Proportion Confused")
conf <- confint(boot_confused, level=0.95)
conf
```
The question we will answer is whether or not the show Dancing with the Stars is confusing based on how many viewers gave it 4 or higher on the confused statement. We first find the actual proportion of confused viewers and then filter the entire dataset into containing only this show and then bootstrap sample 10000 times using the functions filter and do(10000) and resample() respectively. Then we use ggplot to plot a histogram of the distribution of proportions from the bootstrap and confint() to observe the confidence interval at 95%. The show does seem to be statistically significant for viewer confusion. Based on the data above, the actual proportion of confused viewers is only 0.077 in the sample and the estimate is somewhere between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. Since the upper bound of `r round(conf$upper,3)` is not even a quarter of the entire sample, the proportion is not statistically significant, meaning the show does not create confusion for the majority of viewers.

## Problem 4
#### Part A
```{r, echo=F, warning=F, message=F}
mean(rev_ratio~adwords_pause, data=ebay)
diffmean(rev_ratio~adwords_pause, data=ebay)
boot_adpause <- do(10000)*diffmean(rev_ratio~adwords_pause, data=mosaic::resample(ebay, replace=T))
ggplot(data=boot_adpause)+geom_histogram(aes(x=diffmean))+labs(title="Histogram for Difference in Mean between Revenue Ratios based on Ad Pausing", x="Difference in Mean Revenue Ratio")
conf <- confint(boot_adpause, level=0.95)
conf
```
The question we will answer is whether or not pausing ads affects the revenue ratio. We first calculate the actual mean difference and then bootstrap sample 10000 times using the functions do(10000) and resample(). Then we use ggplot to plot a histogram of the distribution of mean differences from the bootstrap and confint() to observe the confidence interval at 95%. Pausing ads seems to be statistically significant for the revenue ratio. Based on the data above, the actual difference in mean between the treatment and control groups is -0.052 in the sample and the estimate is somewhere between `r round(conf$lower,3)` and `r round(conf$upper,3)` with 95% confidence. Since 0 is not included within the confidence interval, the difference in means is statistically significant, meaning pausing ads produces a significantly lower revenue ratio compared to the control group. 


