---
title: "SDS315_HW9"
author: "Tommy Fang EID: hf5829 Repo: https://github.com/tominister/SDS315"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
library(MatchIt)
library(mosaic)
vote=read.csv("turnout.csv")
solder=read.csv("solder.csv")
```

## Problem 1
#### Part A
```{r, echo=F, warning=F, message=F}
prop(voted1998~GOTV_call, data=vote)
vote_boot=do(1000)*diffprop(voted1998~GOTV_call, data=mosaic::resample(vote,replace=T))
ggplot(data=vote_boot)+geom_histogram(aes(x=diffprop))+labs(title="Histogram for Difference in Proportions for Voters in 1998 with and without the GOTV Call", x="Difference in Proportions")
confint(vote_boot, level=0.95)
```


#### Part B
```{r, echo=F, warning=F, message=F}
vote_model=lm(voted1998~voted1996+AGE+MAJORPTY, data=vote)
confint(vote_model, level=0.95)
```

#### Part C
```{r, echo=F, warning=F, message=F}
vote_match = matchit(GOTV_call ~ voted1996+AGE + MAJORPTY, data = vote, ratio=5)
vote_matched = match.data(vote_match)
prop(voted1996~GOTV_call, data=vote_matched)
mean(AGE~GOTV_call, data=vote_matched)
prop(MAJORPTY~GOTV_call, data=vote_matched)

prop(voted1998~GOTV_call, data=vote_matched)
vote_matched_boot=do(1000)*diffprop(voted1998~GOTV_call, data=mosaic::resample(vote_matched,replace=T))
ggplot(data=vote_matched_boot)+geom_histogram(aes(x=diffprop))+labs(title="Histogram for Difference in Proportions for Voters in 1998 with and without the GOTV Call with Matching", x="Difference in Proportions")
confint(vote_matched_boot, level=0.95)
```

## Problem 2
#### Part A
```{r, echo=F, warning=F, message=F}
ggplot(solder,aes(x=factor(Opening),y=skips))+geom_jitter()+stat_summary(fun='mean',color='darkorange')
ggplot(solder, aes(x=factor(Solder),y=skips))+geom_jitter()+stat_summary(fun='mean',color='darkorange')
```

#### Part B
```{r}
solder_model=lm(skips~Opening+Solder+Opening:Solder, data=solder)
confint(solder_model, level=0.95)
```

#### Part C
```{r}
coef(solder_model)
```
Using the number of skips of a board with a large opening and thick solder as a base, it can be seen that thick solders with a medium opening have an offset of around 2.4 more skips and a small opening 5.13 more skips. In addition, a large opening with a thin solder has an offset of 2.28 more skips, and a thin solder with medium and small openings have an offset of 0.74 less skips and 9.65 more skips respectively. 

#### D 
The thin solder with a medium opening is the best recommendation based on the analysis. It can be seen that all boards besides this have a positive offset, meaning the number of skips is greater than that of the base. Since a thin solder and medium opening has the greatest negative offset, it is the best recommendation. 

